Deep Variation Transformation for Foreground Detection

### 2019-02-01 draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.  On branch master  Changes to be committed: 	modified:   draft.log 	modified:   draft.pdf 	modified:   draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.  On branch master  Changes to be committed: 	modified:   draft.aux 	modified:   draft.log 	modified:   draft.pdf 	modified:   draft.tex

\usepackage{cite}
\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{multirow}
\usepackage[unicode,pdftex]{hyperref}
\usepackage{xcolor}

@@

\author{Yongxin Ge, 
        Xinyu Ren, 
        Chenqiu Zhao,
        Anup Basu}

@@

\begin{abstract}
%
% 运动检测的已有方法主要关注于像素值的变化。
Previous approaches to foreground detection generally analyzed the variation of pixel observations.
% 本文中，我们分析了像素的变动，并提出了DPVTL方法。
% In this paper, we focus on transforming the variation into a new space where that there is an obvious difference between the patterns of variation produced by the moving objects and the background,
In this paper, we focus on transforming the variation into another space where the entry of variation is easily classified, using a novel foreground detection method called Deep Pixel Variation Transformation Learning (DPVTL).
% 一个FCN被用来寻求一个变换，可以使变换过后的像素值线性可分。
% 具体来说，我们用一段像素观测值表示pixel variation,并用作网络的输入。 
In particular, the pixel variation is represented by the sequence of pixel space, which is used as the input for a fully convolutional network(FCN) to find a transformation of pixels' variation.
% 接下来，FCN学习像素变动的模式，并接上一个线性分类器给像素打标签。
Then, the FCN is trained to learn the pattern of pixel variations for the transformation, followed by a linear classifier for labeling the pixels as foreground or background.
%    
% XXX 这句话还是有点问题
% 这句话我也没看懂。。。
    \textcolor{red}{
Benefited from the ingenious utilization of deep learning network leading by our clear cognition of essence about foreground detection problem,
    the proposed approach adaptively generates superior performances in diverse nature scenes.}
%
Comprehensive experiments on several standard benchmark demonstrate the superiority of the proposed approach compared with state-of-the-art deep learning and traditional methods.
%
\end{abstract}

@@

% 第二段重点阐述什么是deep variation learning
% 在多样的自然场景中，前景可能产生和背景相似，甚至相同的像素，而这种像素很难去分析
In diversely natural scenes,
it is possible that moving objects produce similar or even the same observations of pixels compared to the background.
% similar to their counterparts of background but actually belong to foreground .
% 如图所示，像素观测值C就和背景的值几乎一模一样，
As shown in the \reffig{idea},
the observation C is closely related to the observations which belong to the background. However, it is actually produced by moving objects and should be classified as foreground.
% 大多数情况下，他都会被划分成背景
Unfortunately, in most cases, it is highly possible that C will be falsely classified due to the similarity with counterparts of the background.
% 我们的就是希望把这个variation 转化到更简单的地方去
In this work, we focus on learning the pattern of pixels' variation and transforming the variations into a new space where the observations are easier to classify, rather than learning a classifier for individual pixels.
As shown in the bottom part of \reffig{idea}, the pattern of a fragment consisting of observations A-D can be learned by the network and transformed into another fragment where these observations are easily and correctly classified as foreground.
% transformatin 之后，就很容易分类了，然后这就是我们的方法的核心了
Based on this, the Deep Pixel Variation Transformation Learning model for foreground detection is proposed.
% motivation
% %实际应用中的挑战
% \todo{the main purpose of the second paragraph is showing our idea. But be careful that you should not mention any details of our method which is the content of third paragraph. Pls re-write this part according to figure 1. The main content should be the description of figure 1, as well as our idea, insight}
% Existed methods have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes. 
% However, foreground detection is still unsolved because of the complexity and the diversity of natural scenes.
% There are many forms of natrual scenes, for example, camera jitter, dynamic background, bad weather, illumination changing, intermittent object motion\cite{CDN2014}. In these situations, the backgrounds are no longer being static, while in fact, the background can be dynamic and complex, which brings some severe challenges to the traditional methods.
% To solve this problem, we bring up a novel conception of variation transformation, wherein the historical observations of each pixel are conceived as a unity, the pixel variation. Each piece of pixel variation contains the complete temporal information of historical observations, which turns out to be our advantage that not only the distribution of observations, but also the temporal coherence plays an important role in the task.
\begin{figure}[!t]	% FIGURE: figure/fig1 
\centering
    \includegraphics[width=\linewidth]{figure/demo.pdf}
    % 图例里描述一下。
    \caption{The demonstration of deep variation transformation. Due to the complexity of natural scenes, the original pixels' variation is hard to classify correctly. After transforming by deep learning network, the pixels in variation become easy to be classified as foreground and background correctly.}
    \label{idea}
\end{figure}
%The demonstration of deep variation transformation. The pixels in the transformed variation become easier to be classified as foreground and background correctly
%本文的想法和优势
% The previous methods have already made great progress in generating some sophisticated background models with given videos. 
% Unfortunately, some instructive clues have been long put aside and neglected, since there is no efficient way to deal with them. 
% For instance, the statistical methods\cite{Stauffer1999} model the pixel-wise distribution of historical observations over time, while having no concerns over the sequential information in a video stream.

@@

%GMM 
% cqzhao: 我没有看到过over time，如果你在trans或者顶会(ICCV,CVPR,ECCV)里找到了论文原话，那你可以用哦。
In particular, the Gaussian Mixture Model (GMM) proposed by Stauffer et al.\ \cite{Stauffer1999} is the most popular approach among pixels-based methods\cite{Goyal2018}.
% 注意英语和汉语的表达习惯
It utilizes a mixture of weighted Gaussians to model the probability distribution of each pixel over a time sequence.
%
\textcolor{red}{Pixels are considered as background if there exists a Gaussian function includes their values with sufficient evidence.} 
%GMM+i
Zivkovic et al.\ \cite{Zivkovic2004} improved the GMM method by utilizing a recursive equation
to automatically update the parameters and adjust the number of components of the mixture needed for each pixel. 
%
%codebook
Kim et al.\cite{Kim2005} presented the codebook method, which records the sampling background values on codewords for each pixel position.
The incoming pixels are compared with these codewords to see if their distances lie within a certain bound. 
%KDE
In addition, a non-parametric background model is proposed by Elgammal et al. \cite{Elgammal2000Non}. 
They assume that each background pixel is drawn from a probability distribution function, which is estimated Kernel Density Estimation space (KDE). 
%Vibe
Another non-parametric method is proposed by Barnich et al. \cite{Barnich2011_2011_TIP}, called the Visual Background Extractor (ViBe). 
%
The background model of ViBe consists of pixel samples from the video stream. 
%
Each pixel in the current frame is compared with sampling pixels from the corresponding background model and labelled as the foreground when there exists sufficient samples with a distance to itself within a certain range. 
%PBAS
To adaptively update the parameters, Hofmann et al.\cite{Hofmann2012Background} improved ViBe by presenting an adaptive threshold, 
which depends on the pixel position and a background dynamics metric.

@@

%me
\section{Foreground Detection via Deep Variation Transformation}
\label{sec4}
In this section, details of the proposed aren explained.
%
The pipeline of the proposed approach is shown in the \reffig{flow_chart},
which can be divided into three parts.
%
First, the procedure generating pixel patches,
which are fed into the network for training as well as the description of pixel variation,
is introduced.
%
Then,
the architecture of the network, which is devised for transforming the variation of pixels' observations, is demonstrated.
%
Next,
a reverse procedure of the generation of training data is used to reconstruct the foreground image from the transformed results.
%
%We explain the production of the pixel patch, 
%which is a specific form of the pixel variation, and the architecture of our network. 
%

@@

% 描述网络结构
%The network used in this work is devised as an end-to-end architecture XXX
\textcolor{red}{The architecture of our FCN for foreground detection is illustrated in \reffig{flow_chart}. 
The proposed FCN contains 6 convolutional layers without pooling, and the filter size of the first five layers is set to $3\times 3$, compared to the last convolutional layer which has a filter size of $1\times 1$. 
We use the Rectified Linear Unit (ReLU) as the activation function after first three convolutional layers. And the Sigmoid Cross Entropy loss function is applied to measures the performance of our network after the last convolutional layer. 
We do not use any other tricks in our network training and the experiment results prove that the proposed approach is feasible and very effective.
After the thresholding calculations, our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without extra optimization mechanism. }

@@

The proposed approach is compared with several existing traditional state-of-the-art foreground detection algorithms, including IUTIS-5\cite{Bianco2017TEC}, SuBSENSE\cite{St-Charles2015SuBSENSE}, WeSamBE\cite{Jiang2017WeSamBE}, sharable GMM the SharedModel\cite{Chen2015SharedModel}, word-dictionaries-based method like PAWCS\cite{Charles2015PAWCS}, SemanticBGS\cite{Braham2017Semantic}, AAPSA\cite{RAMIREZALONSO2016990}, etc. 
Moreover, two deep learning based algorithms are also compared with the proposed approach, which including DeepBS\cite{Babaee2017deep}, and DBMF\cite{Yang2018DBMF}. 
\textcolor{red}{All the results of compared algorithms are provided by authors.}

@@

Quantitative and qualitative comparisons are shown in \reftab{tab1} and  \reffig{results_chart} respectively. 
TO keep the length of this paper XXX, only several typical videos are selected for the qualitative comparisons and discussion. 
In the dynamic background scene, the video ``canoe'' is a typical challenging video which includes a large area of rippling water. 
The main challenge comes from the dynamic background, in which it is hard to describe the background by a single image. 
For this condition, since traditional foreground detection methods such as the SharedModel and the WeSamBE cannot describe the complex dynamical background, they fail to detect the people on the boat, as shown in the \reffig{results_chart}. 
Besides, the detected moving objects of the SharedModel are not accurate in the boundary due to the utilization of texture features. 
In contrast, benefiting from the strong learning ability of Deep Learning networks, DeepBS successfully detects the people. 
Unfortunately, since the DeepBS ignores the fact that a single background is not enough to describe the dynamic background, even this algorithm suffers from poor detection of the boat shape. 
In contrast, the proposed approach performs superior to others in this scene, since the essence of foreground detection is considered as a binary classification of pixels' observation over a time sequence. 
Based on this insight, the FCN network focuses on learning the patterns of pixel variation rather than a static background image.
Thus proposed approach achieves promising performance for the canoe video.

@@

The quantitative evaluation of the proposed approach on CDnet 2014 is shown in \reftab{tab1}. 
It can be seen that the proposed approach significantly outperforms all of the compared state-of-the-art algorithms in most of complex scenes and achieves 11.37\% gain in FM over the second one on the whole dataset. 
\textcolor{red}{Moreover, in order to compare the proposed approach with the DBMF, which is also based on deep learning and only publish their results in  specific videos. 
The proposed approach has also ran in these videos and the results are shown in Table 2. 
Again, the proposed approach has noticeably better performance than the DBMF and some other classical background approaches.}

@@

\section{Conclusion}
\label{sec6}
In this paper, we proposed a novel foreground detection approach based on proposed variation transformation learning. 
The DPVTL model includes a FCN network and a novel variation transformation learning framework, 
which allows us to efficiently combine the temporal coherence and distribution information of pixels over a long period of time. 
Comparisons with other traditional and deep learning methods shows that DPVTL significantly improves performance on several challenging scenes.
%The future work will be focused on improving the DPVTL in terms of network architecture updating and integration of local spatial coherence.

% \section{Conclusions}
% In this paper,
% we proposed the IFB framework for foreground detection for the case of a freely moving camera.
% Unlike previous work in which attempts were made to improve the accuracy of the estimation of motion,
% our IFB focuses on integrating rough foreground and background cues for foreground segmentation.
% In particular, 
% foreground cues are detected by a GMM model with the estimation of background motion,
% while background cues are captured from spatio-temporal features filtered by homography transformation,
% where the SURF\cite{2006_SURF}, KAZE\cite{2012_KAZE}, SIFT\cite{lowe2004distinctive} features are used as examples.
% % the geometric constraints between the SIFT features.
% Then, super-pixels under multiple levels are utilized to integrate these cues.
% The efficiency of IFB results from the complementarity between foreground and background cues.
% The accuracy of the proposed approach is improved though the utilization of super-pixels under multiple levels.
% A comprehensive experiment to compare our results with the state-of-the-art shows the efficiency of our framework and points to its potential for use in practical applications.
% 
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

>>>>

\usepackage{cite}
\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{multirow}
\usepackage[unicode,pdftex]{hyperref}
\usepackage{xcolor}
\usepackage{setspace}

@@

\author{Yongxin Ge, 
        Xinyu Ren, 
        Chenqiu Zhao,
        Anup Basu
        \thanks{Yongxin Ge is with School of Software Engineering, Chongqing University, Chongqing (401331), PR China.}
        \thanks{Xinyu Ren is with School of Software Engineering, Chongqing University, Chongqing (401331), PR China.}
        \thanks{Chenqiu Zhao is with Department of Computing Science, University of Alberta (T6G 2E1), Canada.}
        \thanks{Anup Basu is with Department of Computing Science, University of Alberta (T6G 2E1), Canada.}
        }

@@

\begin{spacing}{2.0}
\begin{abstract}
%
% 运动检测的已有方法主要关注于像素值的变化。
Previous approaches to foreground detection generally analyzed the variation of pixel observations.
% 本文中，我们分析了像素的变动，并提出了DPVTL方法。
% In this paper, we focus on transforming the variation into a new space where that there is an obvious difference between the patterns of variation produced by the moving objects and the background,
In this paper, we focus on transforming the variation into another space where the entry of variation is easily classified, using a novel foreground detection method called Deep Pixel Variation Transformation Learning (DPVTL).
% 一个FCN被用来寻求一个变换，可以使变换过后的像素值线性可分。
% 具体来说，我们用一段像素观测值表示pixel variation,并用作网络的输入。 
In particular, the pixel variation is represented by the sequence of pixel space, which is used as the input for a fully convolutional network(FCN) to find a transformation of pixels' variation.
% 接下来，FCN学习像素变动的模式，并接上一个线性分类器给像素打标签。
Then, the FCN is trained to learn the pattern of pixel variations for the transformation, followed by a linear classifier for labeling the pixels as foreground or background.
%    
% XXX 这句话还是有点问题
% 这句话我也没看懂。。。
Due to the global analyse of pixel variations and the strong learning ability of deep learning network,
the proposed approach adaptively learned a good transformation from pixel variation to labels and generates well performances in diverse natural scenes.
%    \textcolor{red}{
% Benefited from the ingenious utilization of deep learning network leading by our clear cognition of essence about foreground detection problem,
%    the proposed approach adaptively generates superior performances in diverse nature scenes.}
%
Comprehensive experiments on several standard benchmark demonstrate the superiority of the proposed approach compared with state-of-the-art deep learning and traditional methods.
%
\end{abstract}

@@

% 第二段重点阐述什么是deep variation learning
% 在多样的自然场景中，前景可能产生和背景相似，甚至相同的像素，而这种像素很难去分析
In diversely natural scenes,
it is possible that moving objects produce similar or even the same observations of pixels compared to the background.
% similar to their counterparts of background but actually belong to foreground .
% 如图所示，像素观测值C就和背景的值几乎一模一样，
As shown in the \reffig{idea},
the observation C is closely related to the observations which belong to the background. However, it is actually produced by moving objects and should be classified as foreground.
% 大多数情况下，他都会被划分成背景
Unfortunately, in most cases, it is quite possible that C will be falsely classified due to the similarity with counterparts of the background.
% 我们的就是希望把这个variation 转化到更简单的地方去
In this work, we focus on learning the pattern of pixels' variation and transforming the variations into a new space where the observations are easier to classify, rather than learning a classifier for individual pixels.
As shown in the bottom part of \reffig{idea}, the pattern of a fragment consisting of observations A-D can be learned by the network and transformed into another fragment where these observations are easily and correctly classified as foreground.
% transformatin 之后，就很容易分类了，然后这就是我们的方法的核心了
Based on this, the Deep Pixel Variation Transformation Learning model for foreground detection is proposed.
% motivation
% %实际应用中的挑战
% \todo{the main purpose of the second paragraph is showing our idea. But be careful that you should not mention any details of our method which is the content of third paragraph. Pls re-write this part according to figure 1. The main content should be the description of figure 1, as well as our idea, insight}
% Existed methods have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes. 
% However, foreground detection is still unsolved because of the complexity and the diversity of natural scenes.
% There are many forms of natrual scenes, for example, camera jitter, dynamic background, bad weather, illumination changing, intermittent object motion\cite{CDN2014}. In these situations, the backgrounds are no longer being static, while in fact, the background can be dynamic and complex, which brings some severe challenges to the traditional methods.
% To solve this problem, we bring up a novel conception of variation transformation, wherein the historical observations of each pixel are conceived as a unity, the pixel variation. Each piece of pixel variation contains the complete temporal information of historical observations, which turns out to be our advantage that not only the distribution of observations, but also the temporal coherence plays an important role in the task.
\begin{figure}[!t]	% FIGURE: figure/fig1 
\centering
    \includegraphics[width=\linewidth]{figure/demo.pdf}
    % 图例里描述一下。
    \caption{The demonstration of deep variation transformation. Due to the complexity of natural scenes, the original pixels' variation is hard to classify correctly. After transforming by deep learning network, the pixels in variation become easy to be classified as foreground and background correctly.}
    \label{idea}
\end{figure}
%The demonstration of deep variation transformation. The pixels in the transformed variation become easier to be classified as foreground and background correctly
%本文的想法和优势
% The previous methods have already made great progress in generating some sophisticated background models with given videos. 
% Unfortunately, some instructive clues have been long put aside and neglected, since there is no efficient way to deal with them. 
% For instance, the statistical methods\cite{Stauffer1999} model the pixel-wise distribution of historical observations over time, while having no concerns over the sequential information in a video stream.

@@

%GMM 
% cqzhao: 我没有看到过over time，如果你在trans或者顶会(ICCV,CVPR,ECCV)里找到了论文原话，那你可以用哦。
In particular, the Gaussian Mixture Model (GMM) proposed by Stauffer et al.\ \cite{Stauffer1999} is the most popular approach among pixels-based methods\cite{Goyal2018}.
% 注意英语和汉语的表达习惯
It utilizes a mixture of weighted Gaussians to model the probability distribution of each pixel over a time sequence.
%
Pixels are considered as background when the probability generated by Gaussians are higher than a user threshold.
% \textcolor{red}{Pixels are considered as background if there exists a Gaussian function includes their values with sufficient evidence.} 
%GMM+i
Zivkovic et al.\ \cite{Zivkovic2004} improved the GMM method by utilizing a recursive equation
to automatically update the parameters and adjust the number of components of the mixture needed for each pixel. 
%
%codebook
Kim et al.\cite{Kim2005} presented the codebook method, which records the sampling background values on codewords for each pixel position.
The incoming pixels are compared with these codewords to see if their distances lie within a certain bound. 
%KDE
In addition, a non-parametric background model is proposed by Elgammal et al. \cite{Elgammal2000Non}. 
They assume that each background pixel is drawn from a probability distribution function, which is estimated Kernel Density Estimation space (KDE). 
%Vibe
Another non-parametric method is proposed by Barnich et al. \cite{Barnich2011_2011_TIP}, called the Visual Background Extractor (ViBe). 
%
The background model of ViBe consists of pixel samples from the video stream. 
%
Each pixel in the current frame is compared with sampling pixels from the corresponding background model and labelled as the foreground when there exists sufficient samples with a distance to itself within a certain range. 
%PBAS
To adaptively update the parameters, Hofmann et al.\cite{Hofmann2012Background} improved ViBe by presenting an adaptive threshold, 
which depends on the pixel position and a background dynamics metric.

@@

%me
\section{Foreground Detection via Deep Variation Transformation}
\label{sec4}
In this section, details of the proposed approach are explained.
%
The pipeline of the proposed approach is shown in the \reffig{flow_chart},
which can be divided into three parts.
%
First, the procedure generating pixel patches,
which are fed into the network for training as well as the description of pixel variation,
is introduced.
%
Then,
the architecture of the network, which is devised for transforming the variation of pixels' observations, is demonstrated.
%
Next,
a reverse procedure of the generation of training data is used to reconstruct the foreground image from the transformed results.
%
%We explain the production of the pixel patch, 
%which is a specific form of the pixel variation, and the architecture of our network. 
%

@@

% 描述网络结构
%The network used in this work is devised as an end-to-end architecture XXX
The architecture of our FCN for foreground detection is illustrated in \reffig{flow_chart}. 
The proposed FCN contains 6 convolutional layers without pooling, and the filter size of the first five layers is set to $3\times 3$, compared to the last convolutional layer which has a filter size of $1\times 1$. 
We use the Rectified Linear Unit (ReLU) as the activation function after first three convolutional layers，
and the Sigmoid Cross Entropy loss function is applied to measures the performance of our network after the last convolutional layer. 
We do not use any other tricks in our network training and the experiment results prove that the proposed approach is feasible and very effective.
After the thresholding calculations, our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without extra optimization mechanism.

@@

The proposed approach is compared with several existing traditional state-of-the-art foreground detection algorithms, including IUTIS-5\cite{Bianco2017TEC}, SuBSENSE\cite{St-Charles2015SuBSENSE}, WeSamBE\cite{Jiang2017WeSamBE}, sharable GMM the SharedModel\cite{Chen2015SharedModel}, word-dictionaries-based method like PAWCS\cite{Charles2015PAWCS}, SemanticBGS\cite{Braham2017Semantic}, AAPSA\cite{RAMIREZALONSO2016990}, etc. 
Moreover, two deep learning based algorithms are also compared with the proposed approach, which including DeepBS\cite{Babaee2017deep}, and DBMF\cite{Yang2018DBMF}. 
The results of the compared algorithms are captured by the implementation provided by authors.
% \textcolor{red}{All the results of compared algorithms are provided by authors.}

@@

Quantitative and qualitative comparisons are shown in \reftab{tab1} and  \reffig{results_chart} respectively. 
To keep the length of this paper reasonable, only several typical videos are selected for the qualitative comparisons and discussion. 
In the dynamic background scene, the video ``canoe'' is a typical challenging video which includes a large area of rippling water. 
The main challenge comes from the dynamic background, in which it is hard to describe the background by a single image. 
For this condition, since traditional foreground detection methods such as the SharedModel and the WeSamBE cannot describe the complex dynamical background, they fail to detect the people on the boat, as shown in the \reffig{results_chart}. 
Besides, the detected moving objects of the SharedModel are not accurate in the boundary due to the utilization of texture features. 
In contrast, benefiting from the strong learning ability of Deep Learning networks, DeepBS successfully detects the people. 
Unfortunately, since the DeepBS ignores the fact that a single background is not enough to describe the dynamic background, even this algorithm suffers from poor detection of the boat shape. 
In contrast, the proposed approach performs superior to others in this scene, since the essence of foreground detection is considered as a binary classification of pixels' observation over a time sequence. 
Based on this insight, the FCN network focuses on learning the patterns of pixel variation rather than a static background image.
Thus proposed approach achieves promising performance for the canoe video.

@@

The quantitative evaluation of the proposed approach on CDnet 2014 is shown in \reftab{tab1}. 
It can be seen that the proposed approach significantly outperforms all of the compared state-of-the-art algorithms in most of complex scenes and achieves 11.37\% gain in FM over the second one on the whole dataset. 
%
Moreover,
since the DBMF only publish their results in several specific videos instead of whole dataset,
the proposed approach has also ran in these videos to compare with the DBMF and the results are shown in Table 2,
which also demonstrates the superiority of the proposed approach.
% \textcolor{red}{Moreover, in order to compare the proposed approach with the DBMF, which is also based on deep learning and only publish their results in  specific videos. 
% The proposed approach has also ran in these videos and the results are shown in Table 2. 
% Again, the proposed approach has noticeably better performance than the DBMF and some other classical background approaches.}

@@

\section{Conclusion}
\label{sec6}
In this paper, we proposed a novel foreground detection approach based on proposed variation transformation learning.
%
The transformation learning focus on learning a transformation from pixel variation to the probability of pixels belong to foreground or background.
%
The global variation pattern of pixel observation is learned for better classification of pixels.
%
In particular, a FCN network and a novel variation transformation learning framework is proposed to efficiently combine the temporal coherence and distribution information of pixels over a long period of time. 
%
Comparisons with other traditional and deep learning methods shows that DPVTL significantly improves performance on several challenging scenes.
%The future work will be focused on improving the DPVTL in terms of network architecture updating and integration of local spatial coherence.

% \section{Conclusions}
% In this paper,
% we proposed the IFB framework for foreground detection for the case of a freely moving camera.
% Unlike previous work in which attempts were made to improve the accuracy of the estimation of motion,
% our IFB focuses on integrating rough foreground and background cues for foreground segmentation.
% In particular, 
% foreground cues are detected by a GMM model with the estimation of background motion,
% while background cues are captured from spatio-temporal features filtered by homography transformation,
% where the SURF\cite{2006_SURF}, KAZE\cite{2012_KAZE}, SIFT\cite{lowe2004distinctive} features are used as examples.
% % the geometric constraints between the SIFT features.
% Then, super-pixels under multiple levels are utilized to integrate these cues.
% The efficiency of IFB results from the complementarity between foreground and background cues.
% The accuracy of the proposed approach is improved though the utilization of super-pixels under multiple levels.
% A comprehensive experiment to compare our results with the state-of-the-art shows the efficiency of our framework and points to its potential for use in practical applications.
%

\end{spacing}

\ifCLASSOPTIONcaptionsoff
  \newpage
\fi
